% This is a template for your written document.
%
% To compile using latexmk on the command line, run the following: 
% latexmk -pdf main.tex

\documentclass[12pt]{article}
\usepackage{setspace}
\singlespace
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{graphicx}

\title{\textbf{DropGuard Lite: Log-Based Bot Risk Scoring Using Real Human Checkout Sessions}}
\author{Godfred Tekpor}

\begin{document}

\maketitle

\section{Introduction}
Limited-release online stores create a buying environment where timing matters a lot. Many users try to purchase the same item at almost the exact same moment, and in that kind of setting even a small speed advantage can determine who gets through checkout first. Bots exploit this by moving through storefront flows more quickly and more consistently than most human shoppers can. While real shoppers can also act fast during a high-demand drop, their sessions usually show more variation, more hesitation, and more signs of ordinary browsing before they attempt to complete a purchase.

This is not only a technical problem. It is also a fairness problem. When the same kinds of automated sessions repeatedly win limited releases, legitimate buyers begin to feel that the system is unfair. Over time that damages trust in the storefront and in the release process itself. For large companies, this problem is often addressed with enterprise anti-bot systems that combine device signals, proprietary telemetry, behavioral data, and constantly updated detection rules \cite{10.1145/3447815}. Smaller sellers, however, usually do not have access to that kind of infrastructure. Even when stronger defenses are available, aggressive anti-bot controls can create a different problem by adding unnecessary friction for legitimate customers \cite{10.1145/3672608.3707741}.

This thesis examines whether a lighter and more explainable approach can still be useful. I present DropGuard Lite, a server-side prototype for bot risk scoring that relies on request logs and reconstructed session behavior rather than heavy client-side instrumentation or black-box detection models. The core idea is simple: instead of judging isolated requests one at a time, the system reconstructs a user session from backend activity, extracts behavioral features from that session, and then assigns a risk score based on patterns that appear suspicious in high-demand checkout settings.

The main research question of this thesis is whether ordinary backend data can support a practical and interpretable method for identifying suspicious fast-path checkout behavior. More specifically, I ask whether sessions that are likely bot-driven can be separated from legitimate human sessions using timing, navigation, and action-based patterns derived from server-observable events.

This project is intentionally modest in scope. I do not claim that one policy, one score, or one feature set can solve the broader web bot problem. I also do not claim that a lightweight scoring system can fully replace stronger multi-layer anti-abuse systems. Instead, I focus on a narrower and more practical question: can a smaller storefront use the data it already collects to make better judgments about which sessions deserve closer attention during a competitive release?

The contribution of this thesis is both practical and methodological. On the practical side, DropGuard Lite offers a clear workflow for ingesting storefront activity, reconstructing sessions, extracting interpretable features, and reviewing suspicious traces. On the methodological side, the thesis argues that session-level behavior matters more than isolated requests when studying fast-path checkout automation. A single cart request or checkout request does not say much by itself. What matters is how quickly it appears, what kind of browsing led up to it, how often nearby actions repeat, and how compressed the overall flow looks compared with ordinary human sessions.

The paper proceeds as follows. Section 2 reviews related work on behavioral bot detection, web log analysis, challenge-based defenses, and heavier commercial approaches. Section 3 provides background on why session reconstruction matters in limited-release commerce. Section 4 explains the methodology and the design of the feature set. Section 5 describes the architecture and implementation of the prototype. Section 6 outlines the evaluation design. Section 7 presents the findings from the current system and explains what they suggest. Section 8 discusses the implications, limitations, and meaning of the results. Section 9 concludes with threats to validity and future work.

\section{Related Work}
Prior work on web bot detection suggests that there is no single universal signal that cleanly separates automated traffic from legitimate user activity. Instead, different strands of research highlight different sources of evidence, each with its own tradeoffs. For this project, four themes are especially important: behavioral detection, server-log analysis, challenge-based defenses, and richer multi-signal detection systems.

One important theme is behavioral bot detection. Research in this area suggests that the way actions unfold over time can reveal more than simple counts of requests or static header information. Timing regularity, short transition windows, and repeated action patterns can all help indicate suspicious activity. Rahman and Tomar, for example, argue that behavior-oriented features can strengthen detection by focusing on how requests are generated rather than only on what resources are requested \cite{rahman2020new}. Tanaka and colleagues similarly show that combining user behavior with other request-level information can improve log-based bot detection \cite{tanaka2020bot}. The main takeaway from this line of work is that suspicious traffic often becomes easier to identify when viewed as a sequence rather than as a collection of independent requests.

A second theme is web log analysis and forensic investigation. This literature matters a great deal for my project because DropGuard Lite is built on the assumption that ordinary backend logs contain meaningful evidence. Stassopoulou and Dikaiakos showed early on that web robot detection could be framed probabilistically using server-side traces \cite{stassopoulou2009web}. Later work by Rahman and Tomar extended that idea by showing that request logs can support bot-oriented forensic analysis even without relying heavily on rich client instrumentation \cite{rahman2020forensic}. This is important because many smaller systems already collect backend logs for monitoring and debugging, which means session-level analysis can potentially be added without requiring a complete redesign of the storefront.

A third area includes challenge-based and rule-based defenses such as CAPTCHAs, queues, thresholds, and other friction mechanisms. These approaches remain common because they are relatively understandable and can block certain forms of abuse. However, they also create usability costs. A CAPTCHA or queue may successfully slow down bots, but it can also frustrate legitimate customers, especially during a time-sensitive release. Recent work such as Swiss Cheese CAPTCHA shows that challenge design continues to evolve, but it also reinforces the larger point that challenge systems involve a tradeoff between protection and user experience \cite{10.1145/3672608.3707741}. This tradeoff is one reason a risk-based approach is appealing. If suspicious sessions can be scored first, stronger friction can be applied more selectively.

A fourth theme is the rise of heavier anti-bot systems that combine multiple streams of evidence, such as device fingerprints, mouse dynamics, browser metadata, and broader telemetry. Iliou and coauthors, for instance, show that behavioral biometrics and log signals together can strengthen advanced web bot detection \cite{10.1145/3447815}. At the same time, later work on bot evasion using deep reinforcement learning makes clear that attackers can adapt to detection strategies over time \cite{10.1145/3538969.3538994}. This matters for my thesis in two ways. First, it shows why simple static rules are rarely enough on their own. Second, it highlights the practical gap between what large commercial systems can do and what smaller storefronts can realistically deploy.

The gap my thesis focuses on is therefore not whether richer systems can outperform simpler ones. They often can. The more relevant question is whether a smaller and more transparent system can still provide meaningful value in practice. Many storefronts need a baseline they can actually understand, inspect, and adjust. A lightweight system that reconstructs sessions, computes interpretable features, and supports human review may be less powerful than enterprise anti-bot infrastructure, but it may still be much more deployable.

My work differs from prior literature in emphasis rather than in claiming a completely new detection principle. The novelty here is the combination of scope, design choice, and deployment target. DropGuard Lite focuses specifically on fast-path checkout behavior in limited-release storefronts. It relies primarily on backend activity rather than heavy telemetry. It treats explainability as a core design requirement rather than an afterthought. And instead of presenting detection as an all-or-nothing classification problem, it frames the output as a session-level risk score that can support different levels of intervention.

In that sense, this project is best understood as a practical middle ground. It sits between naive threshold rules and large commercial anti-bot platforms. The goal is not to compete with the most sophisticated systems. The goal is to show that a smaller system can still capture useful evidence, especially when operators need something they can audit, reason about, and improve over time.

\section{Background}
Drop-based online commerce is built around scarcity, urgency, and competition. A store announces that a limited product will go live at a certain time, and a large number of users attempt to access the site almost simultaneously. Under these conditions, small differences in speed and consistency matter a great deal. A user who reaches checkout a few seconds earlier than another may secure the item, while the slower user misses it entirely. This creates a strong incentive to automate as much of the process as possible.

Fast-path bots are especially relevant in this environment. Rather than simulating broad exploration of the storefront, they are designed to move quickly through a narrow purchase path. In many cases, that means entering product pages immediately, adding an item to cart with minimal browsing, retrying critical endpoints aggressively, and reaching checkout with compressed timing. These patterns are not always exclusive to bots. Highly motivated human users may behave aggressively too, especially when they know a product is likely to sell out. Still, suspicious sessions often show a tighter, shallower, and more mechanically consistent path through the storefront.

This is why session reconstruction matters. Looking at one request at a time strips away the context needed to interpret behavior. A checkout request is perfectly normal in isolation. It becomes more or less suspicious only when placed inside a larger sequence. Did the session browse several pages before checkout, or did it jump into checkout almost immediately? Were there long pauses and normal variation between actions, or was the session tightly compressed? Did it retry cart or payment endpoints repeatedly in a narrow time window? These kinds of questions cannot be answered from individual requests alone \cite{rahman2020forensic,stassopoulou2009web}.

The choice to focus on server-side data is deliberate. It keeps the project grounded in signals that many systems already collect. Web applications often record timestamps, endpoints, HTTP methods, response codes, identifiers, and session-relevant metadata as part of routine monitoring. By using that information, the detection pipeline becomes easier to deploy and easier to explain. If a session is flagged, an operator can review the sequence of requests and understand which behaviors contributed to the score.

This approach also comes with clear limitations. Server-side logs do not capture everything. They cannot directly observe mouse movement, scrolling behavior, or detailed client-side interactions unless those are explicitly instrumented and transmitted. They may also be incomplete or inconsistent depending on how the storefront is implemented. As a result, the scope of DropGuard Lite is intentionally limited to the forms of evidence that are visible from the backend and to the kinds of suspicious behavior that those signals can reasonably capture.

Interpretability is another important part of the background for this project. In many real storefront settings, decisions about anti-bot intervention need to be reviewed and explained. If a session is challenged, delayed, or deprioritized, operators may need to justify why. A policy-based scoring system built from understandable features is useful in that kind of environment because it links decisions back to observable behavior instead of hiding them inside an opaque model. That does not make the system perfect, but it does make it easier to audit and refine.

\section{Methodology}
The methodological goal of DropGuard Lite is to identify suspicious fast-path checkout behavior using reconstructed backend sessions. The system does not attempt to infer intent directly, and it does not rely on advanced fingerprinting or external threat intelligence. Instead, it treats risk scoring as a process of collecting session-level evidence and combining that evidence into a transparent assessment of suspicion.

The first step is event collection. The system records storefront activity related to browsing, cart actions, and checkout behavior. Each event includes basic information such as timestamp, event type, endpoint context, session identifier, and optional metadata. This information is captured through middleware and selected client-connected events, then stored for downstream analysis.

The second step is session reconstruction. Events are grouped into ordered timelines so that user behavior can be interpreted as a sequence. This step is essential because the meaning of most actions depends on what comes before and after them. A cart request that happens after several product views and a reasonable browsing interval may be unremarkable. The same request may look suspicious if it appears almost immediately in a very short and shallow session.

The third step is feature extraction. The features used in this project are designed around three main behavioral dimensions: timing, navigation, and action concentration.

Timing features capture how quickly and how regularly a session moves. These include overall session duration, average inter-event timing, timing compression near critical endpoints, and the degree of burstiness across the session. Fast-path bots often show unusually short sessions and tighter spacing between actions, especially near cart and checkout operations.

Navigation features capture how much of the site a session explores before initiating purchase-critical activity. These include the number of unique pages or endpoint categories visited, the depth of browsing before checkout, and the proportion of the session devoted to general browsing versus purchase-oriented endpoints. Human sessions often show more variation and more exploratory behavior, though this is not universal.

Action-based features capture what the session is trying to do and how often certain actions repeat. These include retry counts near cart and checkout endpoints, repeated action bursts, ratios of browsing actions to purchase actions, and patterns of endpoint concentration. A suspicious session may appear shallow but highly focused, with repeated retries clustered near purchase-critical resources.

The fourth step is risk scoring. In the current prototype, scoring is policy-based rather than learned through a black-box classifier. Each session is evaluated using a set of rules and weighted signals that reflect suspicious patterns. The output is not treated as a final accusation of bot activity. Instead, it is treated as a risk indicator that can support different responses depending on context.

This distinction between evidence and policy is important. The features describe what happened in the session. The thresholds describe how aggressively the system chooses to respond. Different storefronts may tolerate different levels of false positives. A store may decide to use the score only for monitoring, for queue prioritization, for selective friction, or for manual review. Keeping the evidence pipeline separate from the intervention policy makes those tradeoffs more visible and easier to adjust.

The methodology also reflects a design choice about realism. I focus on features that can be extracted reliably and understood easily. A feature that is theoretically useful but too noisy to trust or too obscure to explain is less valuable in a lightweight system. The goal is not to maximize complexity. The goal is to build a scoring approach that is understandable enough to deploy and strong enough to be useful.

Finally, the methodology is scoped to fast-path checkout automation rather than every possible type of web bot. That matters because the relevant signals depend on the problem setting. A bot that scrapes content or mimics browsing for long periods may need a different feature set. In my case, the main concern is suspicious speed, compressed flow, repeated critical actions, and minimal browsing depth during high-demand product releases.

\section{System Design and Implementation}
DropGuard Lite is implemented as a prototype using FastAPI, SQLite, and a lightweight React-based review interface. The architecture is intentionally simple because one of the goals of the project is to show that a usable bot-risk workflow can be built without a heavy infrastructure stack.

The system has four main layers: telemetry intake, storage, analytics, and review. The telemetry layer captures relevant storefront events as users move through browsing, cart, and checkout flows. Middleware records request-level activity, while selected application events add context where useful. These events are then written into storage.

The storage layer is designed around sessions and events. Event records preserve the sequence of actions over time. Session summaries are updated or inserted as activity arrives. Keeping these two views separate makes it easier to both reconstruct detailed traces and compute higher-level behavioral summaries.

The analytics layer transforms raw event logs into session-level outputs. It reconstructs ordered timelines, computes feature summaries, and prepares the data needed for risk scoring. This layer is where the project’s core logic lives. Instead of focusing on individual requests, it operates on the broader history of a session. That makes it possible to identify compressed checkout paths, repeated retries, and shallow navigation patterns that would be difficult to detect from isolated records.

The review layer exposes these outputs through a lightweight interface. Rather than presenting only a final score, the interface makes it possible to inspect event history, feature summaries, and session-level context. This is useful both for evaluation and for explainability. If a session appears suspicious, the reviewer can inspect the sequence directly and understand what contributed to the concern.

The processing pipeline moves through five stages. First, the system ingests incoming events. Second, it updates stored session state. Third, it reconstructs timelines from the recorded data. Fourth, it computes behavioral features. Fifth, it prepares the output for scoring and review. Structuring the system this way keeps the workflow modular and makes it easier to test individual components separately.

At the current stage of development, telemetry capture, session reconstruction, and feature extraction are implemented and working. The scoring layer is partially implemented, and the review workflow is already sufficient for inspecting suspicious and human-like sessions side by side. What remains less mature is the fully integrated mitigation layer. In other words, the project already supports detection-oriented analysis, but it is not yet a production-ready enforcement system.

This distinction matters because I want the thesis to represent the project honestly. The core technical contribution is the session-based analysis pipeline and the risk-scoring framework built on top of it. The project is not claiming to be a finished commercial anti-bot platform. It is a research prototype that demonstrates a deployable direction and makes the design choices visible.

Another important part of the implementation is lifecycle management. Sessions are time-bounded, retention rules are applied to older telemetry, and consent or collection boundaries can be tracked where relevant. These design choices matter for both system quality and responsible deployment. A lightweight anti-abuse system still needs to think carefully about what data it stores, for how long, and for what purpose.

From an engineering perspective, modularity is one of the most useful features of the design. A storefront could adopt the analytics pipeline first for passive monitoring, then later connect risk scores to stronger interventions if the evidence justifies it. That staged deployment path is one of the reasons a prototype like DropGuard Lite can still be practically valuable even before the mitigation pipeline is fully mature.

\section{Evaluation Setup}
The evaluation for this project is designed to answer a practical question: do reconstructed session traces contain enough information to help distinguish suspicious fast-path behavior from legitimate human checkout activity in a limited-release environment?

Because the project is still in progress, this section describes the evaluation design and the way the system will be assessed rather than presenting a completed experimental study. The goal at this stage is to show how the project will be evaluated once the remaining implementation and labeling work are finalized.

The planned evaluation compares two broad categories of sessions. The first category consists of legitimate human sessions collected in the project environment. These sessions represent real browsing and checkout behavior under ordinary or high-intensity conditions. The second category consists of suspicious or bot-like sessions represented through controlled automated traces and rule-labeled patterns. These traces are not meant to represent every possible bot strategy. Instead, they are meant to capture the narrower class of fast-path behavior that DropGuard Lite is designed to study.

The evaluation will focus on three main criteria.

First, I will evaluate separability. This asks whether suspicious sessions and human sessions show meaningful differences in the behavioral features computed by the system. If suspicious sessions consistently move faster, browse less, and concentrate their actions differently, then the feature set is capturing something useful.

Second, I will evaluate interpretability. A session-level scoring system is only useful in practice if operators can understand why a session appears risky. For that reason, the evaluation will include case-level walkthroughs of representative sessions across different risk bands. These walkthroughs will be used to show whether the system’s judgments line up with visible evidence in the trace.

Third, I will evaluate practical usefulness. Even if a feature set shows some statistical difference between groups, that alone does not make it operationally helpful. The more important question is whether the output could realistically support monitoring, manual review, queue placement, or selective friction in a small storefront environment.

The final quantitative version of the evaluation is expected to report precision, recall, false positive tendencies, and confusion patterns, along with ranked review of high-risk sessions. Ranked review matters because many real-world systems do not treat every flagged session equally. Operators often focus first on the sessions that look most suspicious. A useful system should therefore be able to surface high-concern sessions in a way that supports efficient review.

The evaluation will also include sensitivity checks around timing thresholds and event windows. Release behavior can shift quickly during a drop. A threshold that seems reasonable in one time window may behave differently in another. Testing these sensitivities should help reveal whether the scoring logic is robust or whether it is too dependent on a narrow situation.

One of the most important issues in this setup is label quality. If suspicious sessions are mislabeled or if aggressive human sessions are treated too casually, then any downstream result becomes harder to interpret. For that reason, label quality will be treated as part of the validity discussion rather than as a background assumption.

Because this project is a prototype and not a finished commercial detection system, the evaluation is designed to emphasize evidence quality and decision usefulness rather than only headline metrics. The goal is not just to ask whether the model can classify. The goal is to ask whether the scoring approach provides useful and explainable distinctions that a storefront could act on responsibly.

\section{Results and Findings}
At the current stage of the project, the full quantitative evaluation has not yet been completed. For that reason, this section does not claim final performance results. Instead, it summarizes the patterns the current system is built to measure, the kinds of differences that are already visible in early traces, and the findings I expect the completed evaluation to test more formally.

Even in its current form, the prototype already supports telemetry capture, session reconstruction, and feature extraction. That makes it possible to inspect session histories directly and compare how suspicious traces differ from more typical human sessions. From these early comparisons, several patterns appear likely to matter.

The first expected finding is that suspicious fast-path sessions will move into cart and checkout more quickly than ordinary human sessions. In a limited-release setting, a bot designed to purchase as fast as possible would be expected to show very little buildup before purchase-oriented activity begins. Human users may also move quickly, especially during a competitive drop, but their sessions would still be expected to show more variation and less consistently compressed flow.

A second expected finding is that suspicious sessions will display tighter timing between requests, especially around purchase-critical endpoints. If the system works as intended, higher-risk sessions should show shorter inter-event gaps, more burst-like behavior, and more regular timing in sensitive parts of the checkout flow than legitimate sessions typically do.

A third expected finding is that suspicious sessions will show shallower navigation. Compared with human users, they would be expected to visit fewer parts of the storefront, spend less time exploring, and concentrate more of their behavior on endpoints that move them directly toward purchase. This will not be a perfect signal by itself, since some legitimate users may also arrive with a clear goal and browse very little, but it should still contribute useful evidence when interpreted alongside timing and retry behavior.

A fourth expected finding is that suspicious traces will show stronger concentration of repeated actions around cart and checkout endpoints. A fast-path automated session would likely retry certain requests more aggressively than a human shopper, especially under release pressure. If this pattern appears consistently, it would strengthen the case for treating action concentration as one part of the risk score.

At the same time, I expect the completed evaluation to confirm an important limitation: no single feature will be strong enough on its own to separate suspicious behavior from legitimate human activity during a high-demand drop. Timing may help, but some humans are genuinely fast. Navigation depth may help, but some buyers move directly to the product they want. Retry behavior may help, but even legitimate users can repeat actions when a site is slow or under load. The more realistic expectation is that the combination of these signals will be more informative than any one signal on its own.

So, although the final metrics are not yet available, the likely result of the project is not that DropGuard Lite will perfectly identify all bots. A more realistic expectation is that it will produce a useful ranking of session risk, where suspicious sessions cluster toward the high-risk end because they appear tighter, shallower, and more concentrated around purchase-critical behavior than ordinary human sessions. If the evaluation supports that pattern, it would suggest that lightweight server-side scoring can still provide useful judgment in practice even without a heavy telemetry stack.

\section{Analysis and Discussion}
Even before the final quantitative evaluation is complete, the structure of the project already suggests several important points about what the findings are likely to mean.

First, the thesis supports the idea that server-side behavioral evidence can still be useful, even without a large anti-bot infrastructure. Looking at behavior at the session level matters a great deal here. Suspicious activity is more likely to become visible in the overall sequence of actions than in any one request taken by itself. This is one of the main reasons the project is centered on session reconstruction rather than static per-request rules.

Second, the project points toward a middle-ground approach to bot detection. Simpler methods are easier to deploy, easier to inspect, and easier to adjust. At the same time, they are also likely to be less powerful than larger systems that combine many forms of telemetry. Even with that limitation, a simpler system can still be worthwhile, especially for smaller storefronts that need something practical and understandable rather than a large commercial platform.

Third, the project suggests that interpretability should remain central to the design. If the final evaluation shows that high-risk sessions can be explained in terms of visible evidence from timing, navigation, and action concentration, then that would strengthen the case for using risk scoring as a review and triage tool rather than treating it as a hidden classification system. In a storefront setting, that kind of explainability matters because operators may need to understand why a session was flagged.

At the same time, the expected findings also come with clear limitations. Attackers can adapt over time and change the way their sessions look \cite{10.1145/3538969.3538994}. More advanced bots may mimic human pacing, introduce fake browsing depth, or spread behavior across identities. Legitimate users in high-pressure release windows may also resemble suspicious sessions on basic timing features. Because of that, I do not expect the final contribution of this thesis to be a claim that simple scoring solves bot abuse in general. A more reasonable conclusion is that it offers a useful first layer of judgment for a narrower problem setting.

Another likely implication is that selective intervention may be more appropriate than blanket friction. If the final system can identify a smaller set of higher-risk sessions, then a storefront could apply stronger defenses more selectively instead of challenging every user equally \cite{10.1145/3672608.3707741}. That possibility is one of the more practical reasons this kind of session-based system is appealing.

More broadly, the project suggests that there is still value in systems that are modest in scope but strong in transparency. Even if DropGuard Lite ends up being less accurate than a richer enterprise anti-bot system, it may still be far easier for a smaller team to understand, deploy, and improve. In that sense, part of the value of the project lies not only in its eventual results, but also in the workflow it provides from raw logs to explainable session-level review.

\section{Conclusion}
This thesis examines whether session-level scoring based on server logs can help identify suspicious fast-path checkout automation in limited-release online commerce. DropGuard Lite contributes a clear workflow for reconstructing sessions, extracting behavior-based features, and using those features to support risk-informed decisions.

The contribution of the project is practical. It offers a method that smaller storefronts could realistically begin with, even if they do not have access to a large commercial anti-bot platform. The project treats detection as a problem of session behavior rather than isolated requests, and it keeps the scoring logic separate from the response policy so that interventions can be tuned based on context.

There are still important threats to validity. Labels may be imperfect, aggressive human behavior may overlap with suspicious behavior, and results may depend on the particular storefront or release pattern being studied. The quality and detail of the logs also place limits on what the system can infer.

The current prototype has clear limitations as well. It relies on server-observable behavior, may miss more advanced bots that imitate human patterns closely, and is not presented as a complete solution to bot abuse. The final quantitative evaluation is also still in progress.

Future work could strengthen the project in several ways. One direction is broader validation across different storefronts and release settings. Another is the use of more sequence-aware modeling. A third is combining interpretable rules with learned models while still preserving transparency. Thresholds could also be adapted based on the phase of a drop, and the scoring system could be integrated more tightly with queueing or mitigation workflows.

Overall, DropGuard Lite shows that bot-risk scoring built from existing backend data is worth studying as a realistic starting point. It does not replace a full layered anti-abuse program, but it can still provide useful evidence in environments where operators need a system that is understandable, reproducible, and easier to deploy. More broadly, the project offers a concrete path from a research question to a workflow that could be improved over time as stronger evidence and better calibration become available.

\bibliographystyle{acm}
\bibliography{bibliography.bib}

\end{document}
